Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-11 ms.tex
I corrected the reference to the analysis section.

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:ModelFits}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
We summarize our results in Section~\ref{sec:conclusions}.

@@

\section{Analysis}

>>>>

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
We summarize our results in Section~\ref{sec:conclusions}.

@@

\section{Analysis}\label{sec:analysis}
